Microplatforms: Product platforms as code

### 2018-03-14 paper.tex
Correct hyphenation
No numbers for introduction and summary

\usepackage{graphicx}% Include figure files
\usepackage{subcaption}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\section{Introduction}
\label{sec:introduction}

@@

In section \ref{sec:benefits} we outline the goals a good product platform should aim to support. In section \ref{sec:cost} the current approach of using a shared platform is discussed and an alternative (Microplatforms) is suggested in section \ref{sec:microplatforms}, supported by the concept of managing all aspects of it as source code in section \ref{sec:ascode}. Finally, we describe a reference architecture of an example Microplatform in Appendix A.

@@

The ideal situation would therefore be for each product team to be fully in control of their entire product - the application, the platform, the entire life-cycle and everything described in section 1. The only shared dependencies left are the essential ones that have to be shared, i.e. sharing them brings clear benefits (e.g. central systems of record, single sign-on identity providers, source control repositories, artefact registry, etc.). In order for this approach to be practical in a small agile team and safe in the context of a large organisation, we need to leverage as much automation as possible.

@@

\section{\label{sec:summary}Summary}

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{subcaption}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[british]{babel}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\section*{Introduction}
\label{sec:introduction}

@@

In section \ref{sec:benefits} we outline the goals a good product platform should aim to support. In section \ref{sec:cost} the current approach of using a shared platform is discussed and an alternative (Microplatforms) is suggested in section \ref{sec:microplatforms}, supported by the concept of managing all aspects of it as source code in section \ref{sec:ascode}. Finally, we describe a reference architecture of an example Microplatform in Appendix \ref{sec:architecture}.

@@

The ideal situation would therefore be for each product team to be fully in control of their entire product - the application, the platform, the entire life-cycle and everything described in section \ref{sec:benefits}. The only shared dependencies left are the essential ones that have to be shared, i.e. sharing them brings clear benefits (e.g. central systems of record, single sign-on identity providers, source control repositories, artefact registry, etc.). In order for this approach to be practical in a small agile team and safe in the context of a large organisation, we need to leverage as much automation as possible.

@@

\section*{\label{sec:summary}Summary}
